---
title: "Final Project"
output: html_notebook
---

```{r}
#Intalling the packages

install.packages("tidyverse")
install.packages("caTools")
install.packages("neuralnet")
install.packages("kernlab")
```

```{r}
#Loading the libraries 
library(tidyverse)
library(caTools)
library(neuralnet)
library(kernlab)
```

#Data Set 1: Youtube Data 


```{r}
#Reading the CSV
youtube <- read.csv("youtube.csv", stringsAsFactors = TRUE)
view(youtube)
```

```{r}
#Splitting the data and setting train, validation and test
set.seed(123)
youtube$sample <- sample.split(youtube$Subscribers.gained, SplitRatio = .75)
train_youtube<- subset(youtube, sample ==TRUE)
test_youtube <- subset(youtube, sample == FALSE)
```
## SVM
#Create a model that predicts the subscriber gain for any video 


```{r}
#Data Transformation: Make Subscribers Gained a factor for classification
youtube$class <- as.factor(ifelse(youtube$Subscribers.gained <= 100, "Low ",ifelse(youtube$Subscribers.gained <200,"Mid",ifelse(youtube$Subscribers.gained <300,"High","Very High"))))
view(youtube)
```


```{r}
#Training the SVM 
SVMYoutubeModel <- ksvm(Subscribers.gained ~ .,
                      data = train_youtube,
                      kernel = "vanilladot")


#Prediction

SubscriberPrediction <- predict(SVMYoutubeModel, test_youtube)

#Confusion Matric
YoutubeConfusionMatrix <- table(SubscriberPrediction, test_youtube$Subscribers.gained,
                              dnn = c("Prediction", "Actual"))
SubscriberAccurracy <- sum(diag(YoutubeConfusionMatrix))/sum(YoutubeConfusionMatrix)
cat("The Accurracy is:",SubscriberAccurracy)
view(YoutubeConfusionMatrix)
```

#The Accurracy is: 0.01219512


```{r}
#Plotting the Confusion Matrix
plot(YoutubeConfusionMatrix)
```

```{r}
#Making the Matrix a Data Frame
youtubematrix<- data.frame(YoutubeConfusionMatrix)
```

```{r}
#GGPlot of the Subscribers Confusion Matrix 
SVMConfusionMatrixGGPlot1 <- ggplot(data =  youtubematrix, mapping = aes(x = Prediction, y = Actual)) + geom_tile(aes(fill= Freq)) + theme(axis.text.x = element_blank() ,
        axis.ticks.x=element_blank())
SVMConfusionMatrixGGPlot1
```

```{r}
#GGPlot of the Subscribers Confusion Matrix  2 
SVMConfusionMatrixGGPlot2<- ggplot(data =  youtubematrix, mapping = aes(x = Prediction, y = Actual)) + geom_point(aes(color = Freq)) + theme(axis.text.x = element_blank() ,
        axis.ticks.x=element_blank())
SVMConfusionMatrixGGPlot2
```

## Neural Network

#Predict comments added using all numeric variables in the dataset.
#Test for normality.
#Use normalize() function to transform the data if the data is not normal.
#Create a simple ANN with only a single hidden neuron.
#Plot the ANN model.
#Predict using your model.
#Provide correlation between prediction and actual numbers.

```{r}
#See distribution
hist(youtube$Comments.added)
```
```{r}
shapiro.test(test_youtube$Comments.added)

```

# Since  p-value = 6.85e-11 we reject the null hypothesis, and accept the alternative hypothesis. The distribution is considered not normal. We have to normalize
```{r}
#Install normalize
install.packages("normalr") 
library(normalr)
```

```{r}
# Min-Max Scaling
numeric_youtube <-select(youtube,Views, Comments.added, Subscribers, Impressions, Video.publish.time)
summary(numeric_youtube$Comments.added)
```

#Plot the ANN model.

```{r}
#Training and testing set for normalized data 
normalized_train <- numeric_youtube[1:15,]
normalized_test <- numeric_youtube[15:3483,]
```


```{r}
#ANN
ann_model <- neuralnet(formula = Comments.added ~ Views, data = numeric_youtube)
ANNPLOT<- plot(ann_model)
```
## Decision Trees 

#Predict if someone will subscribe to the podcast depending on how many views a video has

#Install Packages

```{r}
install.packages("caret")
install.packages("e1071")
install.packages("rpart")
install.packages("rpart.plot")
install.packages("party")

```

#Load Libraries
```{r}
library(caret)
library(e1071)
library(rpart)
library(rpart.plot)
library(party)
```


```{r}
#Split the Data

set.seed(321)

sampleYoutube = sample.split(youtube$Subscribers.gained, SplitRatio = .75)
train_Youtube_Cart = subset (youtube, sampleYoutube == TRUE)
test_Youtube_Cart = subset(youtube, sampleYoutube == FALSE)


YoutubeRPartModel <- rpart(Subscribers.gained ~ Views, data = train_Youtube_Cart)
YoutubeRPartModel

# Visualization

DecisionTreePlot <- rpart.plot(YoutubeRPartModel, under = TRUE)
DecisionTreePlot
```
## Naive Bayes

```{r}
install.packages("naivebayes")
library(naivebayes)
```

```{r}
#Data Transformation: Make Subscribers Gained a factor for classification
model <- naiveBayes(Subscribers.gained~class, data = youtube)
predNaiveBayes <- predict(model,youtube)
TableNaiveBayes<- table(predNaiveBayes)
view(TableNaiveBayes)
```


```{r}
#Plot Naive Bayes
plot(TableNaiveBayes)
```
```{r}
#Making the Matrix a Data Frame
TableNaiveBayes<- data.frame(TableNaiveBayes)
```

```{r}
GGPlotNaiveBayes <- ggplot(data =  TableNaiveBayes, mapping = aes(x = predNaiveBayes, y = Freq)) + 
  geom_point()+ theme(axis.text.x = element_blank() ,
        axis.ticks.x=element_blank())
GGPlotNaiveBayes
```

#Other GGPlots

```{r}
#Reading the CSV
viewerstates <- read.csv("views_by_state.csv", stringsAsFactors = TRUE)
view(viewerstates)
```



